Baking the Perfect Cookie

### 2022-12-06 paper.Rmd
small updates

Baking is one of the oldest known forms of preparing foods. As techniques and recipes evolved over the years, making baked goods has become as much of a science as it is an art.  The correct measurements of each ingredient that goes into a treat is very precise, and differing from the given instructions from a recipe can lead to drastic changes in the outcome of whatever is being prepared. This project aims to examine the effects that changing several parameters of a chocolate chip cookie recipe has on the diameter of the cookie using a linear regression model.

@@

These ingredients were chosen as they were both essential ingredients for cookies that could influence cookie size. Baking time was also chosen to be investigated since cookies tend to get flatter as they cook.

@@

In total, 18 batches of 3 cookies each were baked for this experiment; yielding a total of 54 cookies overall. For each batch, the baking time, along with the amounts of flour and butter used, were varied according to an experimental design outlined in Table 1. Other ingredients, including eggs, sugar, baking soda, etc., were held constant across batches. Additionally, variables such as oven temperature and oven placement were controlled across batches.  A digital scale was used to precisely measure the quantity of each ingredient (0.1 grams precision). The following recipe was used for this experiment:

@@

Cookies were baked at 350° F for 9 or 12 minutes on a nonstick cookie sheet. A digital timer was used to ensure that each batch of cookies was baked for the appropriate number of minutes.
\newline

**Table 1.** Experimental design.
```{r pressure, echo=FALSE, out.width = '50%', fig.align = "center"}
knitr::include_graphics("table.png")
```

\newpage

## Results

@@

\newpage

>>>>

Baking is one of the oldest known forms of preparing foods. As techniques and recipes evolved over the years, making baked goods has become as much of a science as it is an art. The correct measurements of each ingredient that goes into a baked good is very precise, and differing from the given instructions from a recipe can lead to drastic changes in the characteristics of the baked good that is being prepared. This project aims to examine the effects of changing several parameters of a chocolate chip cookie recipe has on the diameter of the cookie using a linear regression model.

@@

These ingredients were chosen as they were both essential ingredients for cookies that could influence cookie size. Baking time was also chosen to be investigated since we believe that the cookies will tend to get flatter as they cook.

@@

In order to understand the relationship between cookie diameter and flour, butter, and baking time and collect our data, we designed a controlled experiment. We baked cookies with varying levels of butter, flour, and baking time. In total, 18 batches of 3 cookies each were baked for this experiment; yielding a total of 54 cookies overall. For each batch, the baking time, along with the amounts of flour and butter used, were varied according to an experimental design outlined in Table 1. Notably, we baked cookies for two different baking times, three different amounts of butter, and three different amounts of flour. Other ingredients, including eggs, sugar, baking soda, etc., were held constant across batches. Additionally, variables such as oven temperature, cookie weight (20 grams/cookie dough ball), and oven placement were controlled across batches. A digital scale was used to precisely measure the quantity of each ingredient and the final weight of each cookie dough ball (0.1 grams precision). The following recipe was used for this experiment:

@@

Cookies were baked at 350° F for 9 or 12 minutes on a nonstick cookie sheet. A digital timer was used to ensure that each batch of cookies was baked for the appropriate number of minutes. We varied the amount of flour (40-82 grams/batch) and butter (28-56 grams/batch) within what we believe to be a reasonable range of flour and butter to be used in a chocolate chip cookie. 
\newpage
\noindent \textbf{Table 1.} Experimental design.
```{r pressure, echo=FALSE, out.width = '50%', fig.align = "center"}
knitr::include_graphics("table.png")
```
## Results

@@
